CodeBook.md
========================================================

First, we load in the Features & the activity Labels and create vectors of each
```{r}
Features <- read.table(file="./UCI HAR Dataset/features.txt")
Features <- Features$V2
Activity_labels <- read.table(file="./UCI HAR Dataset/activity_labels.txt")
Activity_labels <- Activity_labels$V2
```

Now, we read in the Test Data. We add a new variable to distinguish between the individual subjects & a second new variable labelling the performed activity
```{r}
Test <- read.table(file="./UCI HAR Dataset/test/X_test.txt", col.names=Features, row.names=NULL)
Subject_Test <- read.table(file="./UCI HAR Dataset/test/subject_test.txt")
Test$Subject <- Subject_Test$V1
Activity_Labels_test <- read.table(file="./UCI HAR Dataset/test/y_test.txt")
Test$Activity <- factor(Activity_Labels_test$V1, levels=1:6,labels= Activity_labels)
```


Here, we prform the same steps as before but this time on the training data
```{r}
Train <- read.table(file="./UCI HAR Dataset/train/X_train.txt", col.names=Features, row.names=NULL)
Subject_Train <- read.table(file="./UCI HAR Dataset/train/subject_train.txt")
Train$Subject <- Subject_Train$V1
Activity_Labels_Train <- read.table(file="./UCI HAR Dataset/train/y_train.txt")
Train$Activity <- factor(Activity_Labels_Train$V1, levels=1:6,labels= Activity_labels)
```

This code merges the test with the traind data
```{r}
Data <- rbind(Train, Test)
```

Now, we extract the variables regarding means & standard deviations
```{r}
toMatch <- c("mean()", "std()")
matches <- grep(paste(toMatch,collapse="|"), Features, value=F)
```

The merged data frame is ready now. Let'save it!
```{r}
write.table(x=Data, file='./Tidy Data.csv', sep=",", row.names=F)
```

Now, we create a second dataframe with the Mean & Standard Deviation of all variables & save it as well
```{r}
Means <- colMeans(Data[,1:(ncol(Data) - 2) ])
Standard.Deviation <- apply( Data[,1:(ncol(Data) - 2) ], 2, sd )

    ## New Dataframe with Means & Standard Deviations
DF <- data.frame(Means, stringsAsFactors=F)
DF <- cbind(DF, Standard.Deviation)
write.table(x=DF, file='./Means-SD Data.csv', sep=",", row.names=F)
```
